\documentclass[11pt, a4paper,oneside,openright]{book}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hyperref}
\hypersetup{
  colorlinks=false,
  citecolor=green,
  filecolor=black,
  linkcolor=red,
  urlcolor=cyan
  }

\addtolength{\hoffset}{-2.5cm}
\addtolength{\textwidth}{4.5cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textheight}{4.5cm}

\numberwithin{equation}{section}

\begin{document}

\title{An introductory class to Physical Cosmology for the Science Honors Program}
\author{Sebastian Garcia-Saenz and Andrea Petri}
\date{Columbia University in the City of New York}
\maketitle

\chapter*{Introduction}
Physical Cosmology is the science that studies the universe on its largest scales, much bigger that planets, planetary systems and even galaxies; on these big scales the universe is well approximated by a nearly homogeneous fluid with very small inhomogeneities. This picture is strongly supported by the last two decades of observations of the Cosmic Microwave Background (CMB), a radiation leftover from the Big Bang whose established presence is the main invitation for the developement and study of Cosmology itself. These notes are meant to be a quick overview of this subject, rolling over its most important and interesting aspects. It will be clear from the beginning that classical physics  is not fit for describing the universe at these large scales, so first we need to introduce the necessary tools for an appropriate description of Cosmology, namely Einstein's theory of Relativity (both special and general). Even if this class is not meant to be technical but qualitative, focusing on the physical ideas, we 
first need to introduce some basic mathematical tools needed for a first understanding. Next we will talk about Relativity, again not technically, but focusing on the physical ideas, at the simplest mathematical level allowed; we then start talking about Cosmology, introducing the Friedmann model that describes the homogeneous universe. To fully understand the physics at this level, we will need to know what this universe, in which we live, is made of, and this will lead us in talking about elementary particles and the thermal history of the cosmos from the Big Bang to the present time; we will try to understand the concepts of dark matter, dark energy, and the importance of the CMB in this big picture. By then we will be able to talk about inhomogeneities, the appearence of large scale structure, dark matter filaments, cluster of galaxies, galaxies and stars. The class will end with an overview of some special topics which are deeply connected with Cosmology, such as black holes, active galactic nuclei and 
the concept of inflation. 

\tableofcontents

\include{Chapter1}
\include{Chapter2}
\include{Chapter3}
\include{Chapter4}
\include{Chapter5}
\include{Chapter6}
\include{Chapter7}
\include{Chapter8}
\include{Chapter9}
\include{Chapter10}
\include{Chapter11}
\include{Chapter12}

\begin{thebibliography}{99}
\end{thebibliography}

\end{document}